\documentclass[11pt]{article}
\usepackage{amsmath}
\title{Midterm Machine Learning}
\author{Professor Francesco Zuppichini}
\begin{document}
\maketitle
\begin{enumerate}
	\item What is gradient descent? State its generic update rule and show why it can be used in ML
	\item What is a Perceptron? State the forward pass and update rule.
	\item Compute the new weights and bias after one full epoch on a Perpectron with input $x = \begin{pmatrix}
	2 \\ 
	10	
	\end{pmatrix}$, weight $w = \begin{pmatrix}
		1.2 \\ 
		-0.5
	\end{pmatrix}$ and bias $b = 3$.
	\item What is a Neural network? Give a high-level definition.
	\item Which are the hyper-parameters in a Neural Network? 
	\item Which problem can a neural network solves that a perceptron can not? Give at least one example.
	\item State the delta rules for the weights and bias.
	\item Give a definition for the following term: hidden layer, activation function, back-propagation and regression
	\item Quickly define overfitting and underfitting.
	\item Write down \epmh{at least} two activations function and their derivative
	\item What is stochastic gradient descent and what problem can solve?
	\item Define regression problems and classifications. State the relative loss functions
	\item What is Convolutional Neural Network and for what they are used for?
	\item Why a Convolutional Layer is different than a normal one?
	\item Give a definition for the following terms: stride and max-pooling
	\item Why RELU is used in a CNN? (write it down its equation)
	\item Why the last layer is a normal fully connected layer? Why we need softmax in the end?
	\item What is a Recurrent Neural Network? Sketch it down a generic example and give a high-level definition.
	\item State the forward pass and the update rules for weight and bias in a RNN. Give a quick overview.
	\item Vanishing Gradient is a well-know problem in RNN. Explain it.
	\item Why where LSTM introduced?
	\item Draw a LSTM-cell and describe it in deep.
	\item Support Vector Machine are another supervise learning algorithm. Give generic definition.
	\item The simplest SVM is just a binary linear classifier. Sketch an example and give an explanation. Use equations to support your words.
	\item Sketch an example of non-linear separable data before and after the mapping to the feature space. Also, what is it?
	\item What is the kernel? Why it is so important? Do you know any trick that can be done with it?
	\item Explain how the dual problem is stated, what we want to maximise/minimise and how Quadratic Programming can help do that. Do not focus too much on the math
\end{enumerate}
\end{document}
